Adaptive broadcast tree for multicores

### 2013-05-07 visu_hierarchy.tex
Oops some files missing

\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (130mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (140mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (150mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (110mm,240mm) {};
\draw[->] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (120mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (130mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (131mm,255mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (141mm,270mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (141mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (160mm,120mm) {};
\draw[->] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (170mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (180mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (190mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (200mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (210mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (220mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (170mm,300mm) {};
\draw[->] (s_4_20.center) -- (r_4_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (180mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (190mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (200mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (181mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (191mm,315mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (191mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (201mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (201mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (211mm,345mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (220mm,180mm) {};
\draw[->] (s_8_12.center) -- (r_8_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (230mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (240mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (250mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (230mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (240mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (250mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (260mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (240mm,420mm) {};
\draw[->] (s_8_28.center) -- (r_8_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (250mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (260mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (270mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (241mm,195mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (251mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (251mm,375mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (261mm,435mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (261mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (261mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (271mm,450mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (271mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (281mm,465mm) {};

>>>>

\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
\draw[->] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (130mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
\draw[->] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (150mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (130mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (140mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
\draw[->] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (121mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
\draw[->] (s_4_16.center) -- (r_4_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (140mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (160mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (131mm,135mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (141mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (141mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (141mm,315mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
\draw[->] (s_12_28.center) -- (r_12_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (170mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (180mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (151mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (151mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (161mm,345mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (171mm,285mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (181mm,435mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (191mm,450mm) {};

@@

### 2013-05-07 visu_mst_sort.tex
Oops some files missing

\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
\draw[->] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (130mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
\draw[->] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (150mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (130mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (140mm,360mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
\draw[->] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (121mm,150mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
\draw[->] (s_4_16.center) -- (r_4_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (140mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (160mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (131mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (141mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (141mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (141mm,315mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
\draw[->] (s_12_28.center) -- (r_12_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (170mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (180mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (151mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (151mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (161mm,345mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (171mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (181mm,435mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (191mm,450mm) {};

>>>>

\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (70mm,0mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (120mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
\draw[->] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (90mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (110mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (81mm,15mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
\draw[->] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (130mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (140mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (160mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (101mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
\draw[->] (s_4_20.center) -- (r_4_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (120mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (140mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (111mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (121mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (130mm,180mm) {};
\draw[->] (s_8_12.center) -- (r_8_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (131mm,315mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (131mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};

@@

@@

\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (170mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (150mm,420mm) {};
\draw[->] (s_8_28.center) -- (r_8_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (180mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (151mm,345mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (151mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (171mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (181mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (191mm,465mm) {};

@@
